\documentclass[11pt]{amsart}
    \topmargin -.5 in
    \textheight 9.0in
    \textwidth 6.25 in
    \oddsidemargin 0 in
    \evensidemargin 0 in
   
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{tikz}
%\usepackage{nth}


\newenvironment{graph}[1][scale=1]{
\begin{tikzpicture}[#1]
\tikzstyle{vertex}=[circle, draw, fill, inner sep=0pt, minimum size=4pt]%
\tikzstyle{bigvtx}=[circle, draw, fill, inner sep=0pt, minimum size=6pt]%
\tikzstyle{every path}=[line width=0.5pt]%
}{\end{tikzpicture}}


\begin{document}
\title{Homework 2: \S1.1,1.2 \qquad Due February 1}
\author{}
\date{}
\maketitle
\thispagestyle{empty}

\noindent Name:~\hrulefill~~\\

\begin{itemize}
\item Refer to the syllabus regarding allowed collaboration on this homework assignment.
\item Refer to other homework instructions and suggestions posted in Blackboard.
\item All answers must be fully justified.
\item Your homework should be neatly written on additional paper; you may attach this cover page if you would like to keep the questions attached to the answers.
\end{itemize}

\bigskip

Turn in four of the following six problems to be graded.

\begin{enumerate}

\item 1.1.17.  Determine all isomorphism classes of simple 4-regular 7-vertex graphs.  \textit{(See also HW1\#3.)}

\item 1.2.7.  Prove that a bipartite graph has a unique bipartition (except for interchanging the two partite sets) if and only if it is connected.

\item 1.2.28ish.  In each graph below, find a bipartite subgraph with the maximum number of edges.  Prove that this is the maximum, and determine whether yours is the only bipartite subgraph with this many edges.
\begin{center}
\begin{graph}
\foreach \i in {1,2,3,4,5,6}
{ \node[vertex] (v\i) at (\i,0) {}; }
\node[vertex] (t) at (4,1) {};
\node[vertex] (b) at (3,-1) {};
\draw (v1)--(v6)--(t)--(v1)--(b)--(v6); \draw (v4)--(t);  \draw (v3)--(b);
\end{graph}
\qquad
\begin{graph}
\foreach \i in {1,2,3,4,5,6}
{
  \node[vertex] (b\i) at (\i,0) {};
  \node[vertex] (c\i) at (\i,1) {};
  \draw (b\i)--(c\i);
}
\node[vertex] (t1) at (1.5,2) {};
\node[vertex] (t3) at (3.5,2) {};
\node[vertex] (t5) at (5.5,2) {};
\draw (b1)--(b2)--(b3)--(b4)--(b5)--(b6);
\draw (c2)--(c3); \draw (c4)--(c5);
\draw (c1)--(t1)--(c2); \draw (c3)--(t3)--(c4); \draw (c5)--(t5)--(c6);
\draw (t1)--(t3)--(t5);
\end{graph}
\end{center}

\item 1.2.29.  Let $G$ be a connected simple graph not having $P_4$ or $C_3$ as an induced subgraph.  Prove that $G$ is a complete bipartite graph.

\item 1.2.39.  Let $G$ be a loopless graph with $\delta(G)\geq3$.  Prove that $G$ contains an even cycle.

\item 1.2.40.  Let $P$ and $Q$ be paths of maximum length in a connected graph $G$.  Prove that $P$ and $Q$ have a common vertex.

\vfill
\begin{quotation}
\footnotesize
\end{quotation}
\end{enumerate}
\end{document}

