\documentclass[11pt]{amsart}%10pt for solutions
\usepackage[margin=1in]{geometry}
  
\usepackage{amsmath,amsthm,amssymb}
\usepackage{enumerate}
\usepackage{tikz}
%\usepackage{nth}

\newcommand{\ceil}[1]{\left\lceil#1\right\rceil}
\newcommand{\floor}[1]{\left\lfloor#1\right\rfloor}
\DeclareMathOperator{\rad}{rad}
\DeclareMathOperator{\diam}{diam}


\newenvironment{graph}[1][scale=1]{
\begin{tikzpicture}[#1]
\tikzstyle{vertex}=[circle, draw, fill, inner sep=0pt, minimum size=4pt]%
\tikzstyle{bigvtx}=[circle, draw, fill, inner sep=0pt, minimum size=6pt]%
\tikzstyle{every path}=[line width=0.5pt]%
}{\end{tikzpicture}}


\begin{document}
\title{Math 454\\ Homework 5 \qquad Due February 22}
\author{}
\date{}
\maketitle
\thispagestyle{empty}

%remove for solutions:
\noindent Name:~\hrulefill~~\\

\begin{itemize}
\item Refer to the syllabus regarding allowed collaboration on this homework assignment.
\item Refer to other homework instructions and suggestions posted in Blackboard.
\item All answers must be fully justified.
\item Your homework should be neatly written on additional paper; you may attach this cover page if you would like to keep the questions attached to the answers.
\end{itemize}

\bigskip
Turn in four of the following problems to be graded.
\bigskip
%-----/remove for solutions

\begin{enumerate}
\item (1.4.25) 
\begin{enumerate}
\item Prove that every connected graph has an orientation in which the number of vertices with odd outdegree is at most 1.
\item Use part (a) to prove that a simple connected graph with an even number of edges has a decomposition into copies of $P_3$.
\end{enumerate}

\item (1.4.29) Suppose that $G$ is a graph and $D$ is an orientation of $G$ that is strongly connected.  Prove that if $G$ has an odd cycle $C$, then $D$ also has an odd cycle.  \textit{(Hint: consider each pair of consecutive vertices on $C$; what does strong connectivity of $D$ give you?  You may use the result of Exercise~1.4.4.)}

\item (1.4.38) Prove that there is an $n$-vertex tournament in which every vertex is a king except for $n\in\{2,4\}$.

%\item digraphic sequences, via bigraphic sequences?

\item (2.1.13) Prove that every connected graph with diameter $d$ has an independent set of size $\ceil{(1+d)/2}$.

\item Prove that for every graph $G$, $\rad(G)\leq\diam(G)\leq2\rad(G)$.  (See Exercise~2.1.47.)

\item Prove that the number of leaves in a tree $T$ (with at least two vertices) is equal to \[ 2+\sum_{\substack{v\in V(T):\\d(v)\geq2}} (d(v)-2). \]

\end{enumerate}


\end{document}

