\documentclass{article}
\usepackage[margin=1in]{geometry}

\usepackage{amsthm,amsmath,amssymb}

\newcommand{\floor}[1]{\left\lfloor#1\right\rfloor}
\newcommand{\cp}{\mathbin\Box}

\theoremstyle{definition}
\newtheorem{theorem}{Theorem}

\begin{document}
\thispagestyle{empty}


\begin{theorem}
$\chi(G)\leq \chi_{\ell}(G)$.
\end{theorem}

\begin{theorem}
If $H\subseteq G$, then $\chi(H)\leq \chi(G)$.

Hence $\chi(G)\geq \omega(G)$.
\end{theorem}

\begin{theorem}
$\chi(G)\geq n(G)/\alpha(G)$.
\end{theorem}

\begin{theorem}[greedy bounds]
$\chi_{\ell}(G)\leq \Delta(G)+1$.

If $G$ has degree sequence $d_1, \dotsc, d_n$, then $\chi_{\ell}(G)\leq 1+\max_i \min\{d_i, i-1\}$.

$\chi_{\ell}(G)\leq 1+\max_{H\subseteq G} \delta(H)$.
\end{theorem}

\begin{theorem}
If $D$ is an orientation of $G$ with longest path length $l(D)$, then $\chi(G)\leq 1+l(D)$.  Furthermore, equality is achieved for some orientation.
\end{theorem}

\begin{theorem}[Brooks]
If $G$ is neither complete nor an odd cycle, then $\chi_{\ell}(G)\leq \Delta(G)$.
\end{theorem}

\begin{theorem}[Tur\'an]
The balanced complete $k$-partite graph has the most edges among $K_{k+1}$-free simple graphs.
\end{theorem}

\begin{theorem}
$G$ is $k$-critical if and only if it is connected, has $\chi(G)=k$, and $\chi(G-e)\leq k-1$ for every $e\in E(G)$.
\end{theorem}

\begin{theorem}
The Mycielskian of $G$ is $(k+1)$-chromatic if $G$ is $k$-chromatic.  It is triangle free if $G$ is.  It is color-critical if $G$ is.
\end{theorem}

\begin{theorem}
$\chi(G+H)=\max\{\chi(G),\chi(H)\}$.
$\chi(G\vee H)=\chi(G)+\chi(H)$.
$\chi(G\cp H)=\max\{\chi(G),\chi(H)\}$.

$G\vee H$ is color-critical if both $G$ and $H$ are.
\end{theorem}

\hrule

\begin{theorem}
$M$ is a maximum matching if and only if there are no $M$-augmenting paths.
\end{theorem}

\begin{theorem}[Hall]
An $X,Y$-bigraph has a matching saturating $X$ if and only if for every $S\subseteq X$, $|S|\leq |N(S)|$.
\end{theorem}
\begin{theorem}
Every nontrivial regular bigraph has a perfect matching.
\end{theorem}

\begin{theorem}[weak duality]
Always $\alpha'(G)\leq \beta(G)$.
\end{theorem}
\begin{theorem}[K\"onig-Egerv\'ary]
If $G$ is bipartite, then $\alpha'(G)=\beta(G)$.
\end{theorem}

\begin{theorem}[Tutte]
$G$ has a perfect matching if and only if for every $S\subseteq V(G)$, $|S|\geq o(G-S)$.
\end{theorem}
\begin{theorem}
Every 3-regular graph without a cut edge has a perfect matching.
\end{theorem}
\begin{theorem}
Every nontrivial even regular graph has a 2-factor.
\end{theorem}


\end{document}